Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-13 manuscript.tex
Ligeti concepts short intro

TODO Some introduction: Ligeti citations are self explanatory...

>>>>

The following is a curated list musical concepts that I have collected from Ligeti's interview.
The description of each concept is quoted directly from the interview.
I add additional clarification only when absolutely necessary, as I think that the concepts are relatively self-explanatory, by Ligeti's words.
